Spfy: distributed predictive genomics of E.coli with graph based result linkage

### 2017-08-17 paper-webserver.tex
ADD: something on data storage

Graph databases focus on describing the relationships between different data points, and is one of the emerging \cite{de2015trends} database types used for biological data.
Spfy

Serotyping, VF, AMR predictions are computed within minutes, and results are efficiently stored within the graph.

>>>>

Graph databases focus on describing the relationships between different data points, is one of the emerging \cite{de2015trends} database types used for biological data, and is one of the core building blocks of a semantic web stack \cite{horrocks2005semantic}.
Spfy uses the RDFLib Python library \url{https://rdflib.readthedocs.org/} to represent all data meant for long-term storage.
When serotyping, VF, AMR predictions, and pangenome generation tasks are completed, the results are stored within the graph database.
